Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-25 JASA-template.tex
Small comment on intro (Matthias).
Comments on abstract/intro.

\begin{abstract}
Causal inference using observational data is important in
many fields, including epidemiology, social science, economics, and many more.
The goal of causal inference is to find the causal effect on the subjects
by identifying causal links between the variables and the outcome.
However, estimation of such causal links is extremely 
difficult because the causal effects may vary from subject 
to subject. Unfortunately, modelling the underlying heterogeneity explicitly makes the 
problem practically unsolvable. Additionally, for high dimensional problems,
we often need to find a subset of 
explanatory variables to initiate the treatment. However, current variable selection methods
simply tend to maximise the predictive performance of the outcome model. This can be problematic when information and data are limited,
as the consequence of mistreatment can be harmful. 
So, in this paper, we develop a model for causal inference using
robust Bayesian analysis, to allow for abstention when selecting
explanatory variables.
Our robust Bayesian model uses a set of spike and slab priors 
through prior elicitation to obtain robust estimates for
both the treatment and outcome model. We are specifically interested 
in the sensitivity of the causal effect in the high dimensional causal inference
as well as identifying confounder variables. However, indicator
based confounder selection can be deceptive, especially
when the predictor is strongly associated with either the treatment or 
the outcome, as this increases the posterior expectation of the selection
indicators. To avoid that, we apply a post-hoc selection scheme
which successfully removes negligible non-zero effects from the model,
attaining a smaller set of confounders. Finally, we illustrate
our method using a synthetic dataset.
\end{abstract}

@@

Causal inference concerns estimating the causal
effect of independent variables on a dependent variable. Ideally,
randomised trials are the most efficient way to perform this task.
However, this is not always practical due to, for instance, ethical 
concerns, design cost, population size, to name a few. This
leaves us with observational studies
where data is collected though surveys or record keeping. But this
can be problematic in the presence of confounders, which are variables associated with both the treatment and the outcome.
In such cases, we must be extra cautious as we risk
unwanted bias in the causal effect estimator \cite{rosenbaum83}.
Several authors have tackled the presence of
confounder variables. 
Robins \cite{Robins1986ANA} used a graphical
approach to identify the causal parameters.
Rosenbaum and Robin \cite{rosenbaum1985} suggested a link model to estimate
the propensity scores for all individuals. Subsequently, several other
methods have been proposed based on propensity score matching;
see \cite{winship99,stuart10} for a brief review.

@@

% latex table generated in R 4.3.0 by xtable 1.8-4 package
% Tue May 23 18:29:20 2023
% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Mon Mar 25 09:52:08 2024
\begin{table}[ht]
\centering
\small
\begin{tabular}{r|ccccc|ccccc}
  \hline
 Case&  &  & 1 &  &  &  &  & 2 &  &  \\ 
  \hline
 & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL \\ 
  \hline
25 & 3.06 & 4.18 & -- & -- & 3.98 & 3.61 & 5.12 &  &  & 3.69 \\ 
  30 & 3.47 & 4.31 & -- & -- & 4.01 & 3.42 & 5.40 &  &  & 9.54 \\ 
  35 & 3.24 & 3.53 & -- & -- & 3.99 & 3.69 & 4.93 &  &  & 9.86 \\ 
  40 & 3.61 & 3.83 & -- & -- & 3.99 & 3.77 & 4.42 &  &  & 3.95 \\ 
  45 & 3.80 & 3.87 & -- & -- & 3.95 & 3.67 & 3.96 &  &  & 3.95 \\ 
  50 & 3.81 & 3.87 & 3.99 & 4.01 & 3.99 & 3.77 & 3.86 & 3.72 & 4.93 & 3.94 \\ 
  55 & 3.88 & 3.95 & 3.97 & 4.00 & 3.98 & 3.79 & 3.92 & 3.96 & 3.95 & 3.97 \\ 
  60 & 3.97 & 3.99 & 3.99 & 4.00 & 3.98 & 3.86 & 3.90 & 3.93 & 3.91 & 3.94 \\ 
  65 & 3.96 & 4.00 & 4.00 & 4.02 & 4.00 & 3.91 & 3.94 & 3.95 & 3.94 & 3.94 \\ 
  70 & 3.96 & 3.99 & 4.01 & 4.05 & 4.00 & 3.84 & 3.89 & 3.94 & 3.95 & 3.95 \\ 
  75 & 3.98 & 4.00 & 4.02 & 4.03 & 4.02 & 3.84 & 3.87 & 3.97 & 3.97 & 3.97 \\ 
  80 & 3.98 & 4.00 & 4.02 & 4.05 & 4.01 & 3.87 & 3.89 & 3.95 & 3.96 & 3.96 \\ 
  85 & 3.97 & 4.00 & 4.03 & 4.04 & 4.03 & 3.91 & 3.93 & 3.96 & 3.94 & 3.96 \\ 
  90 & 3.98 & 4.00 & 4.05 & 4.07 & 4.04 & 3.91 & 3.94 & 3.95 & 3.95 & 3.95 \\ 
  95 & 3.97 & 3.99 & 4.02 & 4.05 & 4.04 & 3.92 & 3.93 & 3.97 & 3.97 & 3.97 \\ 
  100 & 3.96 & 3.98 & 4.03 & 4.05 & 4.04 & 3.92 & 3.94 & 3.96 & 3.96 & 3.96 \\ 
  105 & 3.98 & 3.99 & 4.03 & 4.05 & 4.03 & 3.92 & 3.93 & 3.95 & 3.95 & 3.95 \\ 
  110 & 3.98 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.97 \\ 
  115 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.93 & 3.94 & 3.97 & 3.98 & 3.98 \\ 
  120 & 3.99 & 4.00 & 4.04 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  125 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  130 & 3.99 & 3.99 & 4.02 & 4.04 & 4.02 & 3.92 & 3.94 & 3.97 & 3.97 & 3.97 \\ 
  135 & 3.99 & 4.00 & 4.02 & 4.04 & 4.02 & 3.93 & 3.94 & 3.98 & 3.97 & 3.98 \\ 
  140 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  145 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.94 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  150 & 3.99 & 4.00 & 4.02 & 4.02 & 4.02 & 3.93 & 3.95 & 3.98 & 3.98 & 3.98 \\ 
  155 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.98 & 3.98 & 3.99 \\ 
  160 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  165 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.98 & 3.98 \\ 
  170 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.99 & 3.99 \\ 
  175 & 3.99 & 4.00 & 4.03 & 4.05 & 4.04 & 3.95 & 3.95 & 4.00 & 4.00 & 4.00 \\ 
  180 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
  185 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
  190 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
  195 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
  200 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
   \hline
\end{tabular}
\end{table}
\begin{figure}
    \centering
    \includegraphics[width = 0.9\linewidth]{treat_obs.pdf}
    \caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
    \label{fig:comp:trt}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width = 0.9\linewidth]{treat_pred.pdf}
    \caption{Comparison of different methods in estimating the causal effect for varying number of predictors.}
    \label{fig:comp:trt:pred}
\end{figure}

@@

\subcaption*{First scenario: $|\gamma_j|, |\beta_j|>0$ for $j\le 10$}

@@

1 &   0 &   0 &  43 &  &  &  &  &   0 &   0 \\ 
  2 &   0 &   0 &   5 &  &  &  &  &   0 &   0 \\ 
  3 &   0 &   0 &   2 &  &  &  &  &   0 &   0 \\ 
  4 &   0 &   0 &   0 &  &  &  &  &   0 &   0 \\ 
  5 &   0 &   0 &   0 &  &  &  &  &   0 &   0 \\ 
  6 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  15 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 &   0 \\ 
  16 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 &   0 \\ 
  27 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 &   0 \\ 

>>>>

\begin{abstract}
Causal inference using observational data is important in
many fields, including epidemiology, social science, economics, and many more.
The goal of causal inference is to find the causal effect on subjects
by identifying causal links between
%%% MT to TB: changed "the variables and the outcome" to "a (typically large) number of predictor variables and the outcome of a treatment"
%%% please check if you're happy with this
a (typically large) number of predictor variables and the outcome of a treatment.
% the variables and the outcome.
However, estimation of such causal links is extremely 
difficult because the causal effects may vary from subject 
to subject. Unfortunately, modelling the underlying heterogeneity explicitly makes the 
problem practically unsolvable. Additionally, for high dimensional problems,
we often need to find a subset of 
explanatory variables to initiate the treatment. However, current variable selection methods
simply tend to maximise the predictive performance of the outcome model. This can be problematic when information and data are limited,
as the consequence of mistreatment can be harmful. 
So, in this paper, we develop a model for causal inference using
robust Bayesian analysis, to allow for abstention when selecting
explanatory variables.
Our robust Bayesian model uses a set of spike and slab priors 
through prior elicitation to obtain robust estimates for
both the treatment and outcome model. We are specifically interested 
in the sensitivity of the causal effect in the high dimensional causal inference
as well as identifying confounder variables. However, indicator
based confounder selection can be deceptive, especially
when the predictor is strongly associated with either the treatment or 
the outcome, as this increases the posterior expectation of the selection
indicators. To avoid that, we apply a post-hoc selection scheme
which successfully removes negligible non-zero effects from the model,
attaining a smaller set of confounders. Finally, we illustrate
our method using a synthetic dataset.
\end{abstract}

@@

Causal inference concerns estimating the causal
%%% MT to TB: I changed "dependent variable" to "outcome variable" (I think it's clearer for a general audience, and we talk a lot about the outcome later)
%%% MT to TB: Why do we say "independent variables"? These need not be independent. I've changed this to "predictor variables", I hope that's ok.
effect of predictor variables on an outcome variable,
%%% MT to TB: I added this, please check
as well as identifying which predictors truly affect the outcome.
Ideally,
randomised trials are the most efficient way to perform this task.
However, this is not always practical due to, for instance, ethical 
concerns, design cost, population size, to name a few. This
leaves us with observational studies
where data is collected though surveys or record keeping. But this
can be problematic in the presence of confounders, which are variables associated with both the treatment and the outcome.
In such cases, we must be extra cautious as we risk
unwanted bias in the causal effect estimator \cite{rosenbaum83}.
Several authors have tackled the presence of
confounder variables. 
Robins \cite{Robins1986ANA} used a graphical
approach to identify the causal parameters.
Rosenbaum and Robin \cite{rosenbaum1985} suggested a link model to estimate
the propensity scores for all individuals. Subsequently, several other
methods have been proposed based on propensity score matching;
see \cite{winship99,stuart10} for a brief review.

@@

% latex table generated in R 4.3.0 by xtable 1.8-4 package
% Tue May 23 18:29:20 2023
% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Mon Mar 25 09:52:08 2024
\begin{table}[ht]
\centering
\small
\begin{tabular}{l|ccccc|ccccc}
  \hline
 Case&  &  & 1 &  &  &  &  & 2 &  &  \\ 
  \hline
 & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL \\ 
  \hline
25 & 3.06 & 4.18 & -- & -- & 3.98 & 3.61 & 5.12 &  &  & 3.69 \\ 
  30 & 3.47 & 4.31 & -- & -- & 4.01 & 3.42 & 5.40 &  &  & 9.54 \\ 
  35 & 3.24 & 3.53 & -- & -- & 3.99 & 3.69 & 4.93 &  &  & 9.86 \\ 
  40 & 3.61 & 3.83 & -- & -- & 3.99 & 3.77 & 4.42 &  &  & 3.95 \\ 
  45 & 3.80 & 3.87 & -- & -- & 3.95 & 3.67 & 3.96 &  &  & 3.95 \\ 
  50 & 3.81 & 3.87 & 3.99 & 4.01 & 3.99 & 3.77 & 3.86 & 3.72 & 4.93 & 3.94 \\ 
  55 & 3.88 & 3.95 & 3.97 & 4.00 & 3.98 & 3.79 & 3.92 & 3.96 & 3.95 & 3.97 \\ 
  60 & 3.97 & 3.99 & 3.99 & 4.00 & 3.98 & 3.86 & 3.90 & 3.93 & 3.91 & 3.94 \\ 
  65 & 3.96 & 4.00 & 4.00 & 4.02 & 4.00 & 3.91 & 3.94 & 3.95 & 3.94 & 3.94 \\ 
  70 & 3.96 & 3.99 & 4.01 & 4.05 & 4.00 & 3.84 & 3.89 & 3.94 & 3.95 & 3.95 \\ 
  75 & 3.98 & 4.00 & 4.02 & 4.03 & 4.02 & 3.84 & 3.87 & 3.97 & 3.97 & 3.97 \\ 
  80 & 3.98 & 4.00 & 4.02 & 4.05 & 4.01 & 3.87 & 3.89 & 3.95 & 3.96 & 3.96 \\ 
  85 & 3.97 & 4.00 & 4.03 & 4.04 & 4.03 & 3.91 & 3.93 & 3.96 & 3.94 & 3.96 \\ 
  90 & 3.98 & 4.00 & 4.05 & 4.07 & 4.04 & 3.91 & 3.94 & 3.95 & 3.95 & 3.95 \\ 
  95 & 3.97 & 3.99 & 4.02 & 4.05 & 4.04 & 3.92 & 3.93 & 3.97 & 3.97 & 3.97 \\ 
  100 & 3.96 & 3.98 & 4.03 & 4.05 & 4.04 & 3.92 & 3.94 & 3.96 & 3.96 & 3.96 \\ 
  105 & 3.98 & 3.99 & 4.03 & 4.05 & 4.03 & 3.92 & 3.93 & 3.95 & 3.95 & 3.95 \\ 
  110 & 3.98 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.97 \\ 
  115 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.93 & 3.94 & 3.97 & 3.98 & 3.98 \\ 
  120 & 3.99 & 4.00 & 4.04 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  125 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  130 & 3.99 & 3.99 & 4.02 & 4.04 & 4.02 & 3.92 & 3.94 & 3.97 & 3.97 & 3.97 \\ 
  135 & 3.99 & 4.00 & 4.02 & 4.04 & 4.02 & 3.93 & 3.94 & 3.98 & 3.97 & 3.98 \\ 
  140 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  145 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.94 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  150 & 3.99 & 4.00 & 4.02 & 4.02 & 4.02 & 3.93 & 3.95 & 3.98 & 3.98 & 3.98 \\ 
  155 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.98 & 3.98 & 3.99 \\ 
  160 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  165 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.98 & 3.98 \\ 
  170 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.99 & 3.99 \\ 
  175 & 3.99 & 4.00 & 4.03 & 4.05 & 4.04 & 3.95 & 3.95 & 4.00 & 4.00 & 4.00 \\ 
  180 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
  185 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
  190 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
  195 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
  200 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
   \hline
\end{tabular}
\end{table}
\begin{figure}
    \centering
    \includegraphics[width = 0.9\linewidth]{treat_obs.pdf}
    \caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
    \label{fig:comp:trt}
\end{figure}

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Mon Mar 25 10:08:22 2024
\begin{table}[ht]
\centering
\small
\begin{tabular}{r|ccccc|ccccc}
  \hline
 Case&  &  & 1 &  &  &  &  & 2 &  &  \\ 
  \hline
 & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL & RBCE-u & RBCE-u & SSCE & BSSCE & BSSL \\ 
  \hline
25.00 & 3.06 & 4.18 &  &  & 3.98 & 3.61 & 5.12 &  &  & 3.69 \\ 
  30.00 & 3.47 & 4.31 &  &  & 4.01 & 3.42 & 5.40 &  &  & 9.54 \\ 
  35.00 & 3.24 & 3.53 &  &  & 3.99 & 3.69 & 4.93 &  &  & 9.86 \\ 
  40.00 & 3.61 & 3.83 &  &  & 3.99 & 3.77 & 4.42 &  &  & 3.95 \\ 
  45.00 & 3.80 & 3.87 &  &  & 3.95 & 3.67 & 3.96 &  &  & 3.95 \\ 
  50.00 & 3.81 & 3.87 & 3.99 & 4.01 & 3.99 & 3.77 & 3.86 & 3.72 & 4.93 & 3.94 \\ 
  55.00 & 3.88 & 3.95 & 3.97 & 4.00 & 3.98 & 3.79 & 3.92 & 3.96 & 3.95 & 3.97 \\ 
  60.00 & 3.97 & 3.99 & 3.99 & 4.00 & 3.98 & 3.86 & 3.90 & 3.93 & 3.91 & 3.94 \\ 
  65.00 & 3.96 & 4.00 & 4.00 & 4.02 & 4.00 & 3.91 & 3.94 & 3.95 & 3.94 & 3.94 \\ 
  70.00 & 3.96 & 3.99 & 4.01 & 4.05 & 4.00 & 3.84 & 3.89 & 3.94 & 3.95 & 3.95 \\ 
  75.00 & 3.98 & 4.00 & 4.02 & 4.03 & 4.02 & 3.84 & 3.87 & 3.97 & 3.97 & 3.97 \\ 
  80.00 & 3.98 & 4.00 & 4.02 & 4.05 & 4.01 & 3.87 & 3.89 & 3.95 & 3.96 & 3.96 \\ 
  85.00 & 3.97 & 4.00 & 4.03 & 4.04 & 4.03 & 3.91 & 3.93 & 3.96 & 3.94 & 3.96 \\ 
  90.00 & 3.98 & 4.00 & 4.05 & 4.07 & 4.04 & 3.91 & 3.94 & 3.95 & 3.95 & 3.95 \\ 
  95.00 & 3.97 & 3.99 & 4.02 & 4.05 & 4.04 & 3.92 & 3.93 & 3.97 & 3.97 & 3.97 \\ 
  100.00 & 3.96 & 3.98 & 4.03 & 4.05 & 4.04 & 3.92 & 3.94 & 3.96 & 3.96 & 3.96 \\ 
  105.00 & 3.98 & 3.99 & 4.03 & 4.05 & 4.03 & 3.92 & 3.93 & 3.95 & 3.95 & 3.95 \\ 
  110.00 & 3.98 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.97 \\ 
  115.00 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.93 & 3.94 & 3.97 & 3.98 & 3.98 \\ 
  120.00 & 3.99 & 4.00 & 4.04 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  125.00 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  130.00 & 3.99 & 3.99 & 4.02 & 4.04 & 4.02 & 3.92 & 3.94 & 3.97 & 3.97 & 3.97 \\ 
  135.00 & 3.99 & 4.00 & 4.02 & 4.04 & 4.02 & 3.93 & 3.94 & 3.98 & 3.97 & 3.98 \\ 
  140.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  145.00 & 3.99 & 4.00 & 4.03 & 4.04 & 4.03 & 3.94 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  150.00 & 3.99 & 4.00 & 4.02 & 4.02 & 4.02 & 3.93 & 3.95 & 3.98 & 3.98 & 3.98 \\ 
  155.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.98 & 3.98 & 3.99 \\ 
  160.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.93 & 3.94 & 3.98 & 3.98 & 3.98 \\ 
  165.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.98 & 3.98 \\ 
  170.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.94 & 3.95 & 3.99 & 3.99 & 3.99 \\ 
  175.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.04 & 3.95 & 3.95 & 4.00 & 4.00 & 4.00 \\ 
  180.00 & 3.99 & 4.00 & 4.03 & 4.05 & 4.03 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
  185.00 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
  190.00 & 3.99 & 4.00 & 4.04 & 4.06 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
  195.00 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 4.00 & 3.99 & 3.99 \\ 
  200.00 & 3.99 & 4.00 & 4.04 & 4.05 & 4.04 & 3.95 & 3.96 & 3.99 & 3.99 & 3.99 \\ 
   \hline
\end{tabular}
\end{table}
\begin{figure}
    \centering
    \includegraphics[width = 0.9\linewidth]{treat_pred.pdf}
    \caption{Comparison of different methods in estimating the causal effect for varying number of predictors.}
    \label{fig:comp:trt:pred}
\end{figure}

@@

\small

@@

25 &   0 &   0 &  43 & 8.6 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0&   0  \\ 
  30 &   0 &   0 &   5 & 1 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0 \\ 
  35 &   0 &   0 &   2 & .4 & -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0 \\ 
  40 &   0 &   0 &   0 & 0 &  -- &  --  &  -- &  --  &  -- &  --  &   0 &   0 &   0 \\ 
  45 &   0 &   0 &   0 & 0 & -- &  --  &  -- &  --  &  -- &  --  &    0 &   0 &   0 \\ 
  50 &   0 &   0 &   0 & 0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  55 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  60 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  65 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  70 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  75 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  80 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  85 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  90 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  95 &   0 &   0 &   0 &  0 &  1 &   0 & 1 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  100 &   0 &   0 &   0 &  0 &  1 &   0 & 1 &  0 &   0 &   0 &   0 &   0 &   0 \\ 
  105 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  110 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0&   0 &   0 &   0  &   0 \\ 
  115 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  120 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  125 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  130 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  135 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  140 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  145 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  150 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  155 &   0 &   0 &   0 &  0 &  1 &   0 & 1 &  0 &   0 &   0 &   0 &   0 &   0 \\ 
  160 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  165 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  170 &   0 &   0 &   0 &  0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  175 &   0 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  180 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  185 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  190 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  195 &   0 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  200 &   0 &   0 &   0 &   0 &  0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
